\documentclass[11pt,a4paper,twocolumn]{article}

% ============================================================================
% Packages
% ============================================================================
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{float}
\usepackage{listings}
\usepackage{enumitem}
\usepackage[margin=2cm]{geometry}
\usepackage{fancyhdr}
\usepackage{titlesec}
\usepackage{caption}
\usepackage{tikz}
\usetikzlibrary{arrows.meta,positioning,shapes.geometric,calc,fit,backgrounds}

% ============================================================================
% Colors & Styling
% ============================================================================
\definecolor{qnkblue}{RGB}{20,80,160}
\definecolor{qnkgold}{RGB}{180,140,40}
\definecolor{qnkdark}{RGB}{30,30,45}
\definecolor{qnkgreen}{RGB}{40,160,80}
\definecolor{qnkred}{RGB}{180,40,40}
\definecolor{codebg}{RGB}{245,245,250}

\hypersetup{
    colorlinks=true,
    linkcolor=qnkblue,
    citecolor=qnkblue,
    urlcolor=qnkblue
}

\lstdefinelanguage{Rust}{
    keywords={let,mut,fn,pub,struct,enum,match,if,else,for,while,loop,return,use,mod,impl,trait,where,type,const,static,async,await,move,ref,self,super,crate,as,in,unsafe},
    morecomment=[l]{//},
    morecomment=[s]{/*}{*/},
    morestring=[b]",
    sensitive=true,
}

\lstset{
    basicstyle=\ttfamily\scriptsize,
    backgroundcolor=\color{codebg},
    frame=single,
    framerule=0.3pt,
    breaklines=true,
    columns=fullflexible,
    keywordstyle=\color{qnkblue}\bfseries,
    commentstyle=\color{gray}\itshape,
    stringstyle=\color{qnkgreen},
}

\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\small\textcolor{gray}{Q-NarwhalKnight Infrastructure}}
\fancyhead[R]{\small\textcolor{gray}{v6.0.3 -- February 2026}}
\fancyfoot[C]{\thepage}

\titleformat{\section}{\large\bfseries\color{qnkblue}}{\thesection}{1em}{}
\titleformat{\subsection}{\normalsize\bfseries\color{qnkdark}}{\thesubsection}{1em}{}
\titleformat{\subsubsection}{\small\bfseries\color{qnkdark}}{\thesubsubsection}{1em}{}

% ============================================================================
% Document
% ============================================================================
\begin{document}

% ============================================================================
% Title
% ============================================================================
\twocolumn[
\centering
\vspace{1cm}
{\huge\bfseries\color{qnkblue} Q-NarwhalKnight: Zero-Downtime
Deployment Infrastructure, Bio-Integrated
Consensus \& Cross-Node State Synchronization\par}

\vspace{0.8cm}

{\large Quillon Research Laboratory\par}
{\normalsize \texttt{research@quillon.xyz}\par}

\vspace{0.5cm}

{\normalsize February 11, 2026 \quad|\quad Version 6.0.3\par}

\vspace{0.6cm}

\rule{0.85\textwidth}{0.4pt}

\vspace{0.4cm}

\begin{minipage}{0.85\textwidth}
\textbf{Abstract.}
We present the production infrastructure powering Q-NarwhalKnight, a post-quantum
DAG-BFT blockchain with bio-integrated consensus extensions. This paper details three
interconnected systems: (1)~a three-server High-Availability rolling deployment pipeline
achieving zero-downtime upgrades with automatic rollback, (2)~the Water Robot swarm
architecture employing string-theoretic resonance consensus and spectral Byzantine fault
detection for bio-integrated autonomous coordination, and (3)~an empirical analysis of
cross-node state synchronization revealing that DeFi state (pools, prices, tokens) achieves
100\% consistency while block-level consensus exhibits height divergence of up to $10^5$ blocks
under memory-constrained conditions. We propose a four-phase remediation timeline culminating
in full deterministic state synchronization by Q3~2026, addressing the fundamental challenge
of maintaining consistent distributed state across heterogeneous hardware environments.
\end{minipage}

\vspace{0.6cm}
\rule{0.85\textwidth}{0.4pt}
\vspace{0.8cm}
]

% ============================================================================
% 1. Introduction
% ============================================================================
\section{Introduction}

Deploying blockchain infrastructure to production demands guarantees that traditional
web services do not require: every upgrade risks consensus divergence, balance corruption,
or chain splits that could result in permanent loss of user funds. Q-NarwhalKnight
addresses these challenges through a layered architecture combining:

\begin{itemize}[nosep,leftmargin=*]
    \item \textbf{Rolling deployment pipeline} -- Three-server canary-promote-restore
          workflow with automatic health verification at each stage.
    \item \textbf{RAM-adaptive storage} -- Auto-detection of system memory with tiered
          RocksDB configuration preventing OOM kills on heterogeneous hardware.
    \item \textbf{Water Robot consensus} -- Bio-integrated swarm intelligence using
          string-theoretic resonance for Byzantine fault detection.
    \item \textbf{P2P state propagation} -- Gossipsub-based DeFi state replication
          achieving measured 100\% consistency across nodes.
\end{itemize}

Section~\ref{sec:pipeline} describes the deployment pipeline architecture.
Section~\ref{sec:waterrobots} presents the Water Robot coordination mechanism.
Section~\ref{sec:sync} provides empirical synchronization analysis.
Section~\ref{sec:roadmap} proposes a remediation timeline.

% ============================================================================
% 2. HA Deployment Pipeline
% ============================================================================
\section{High-Availability Rolling Deployment Pipeline}
\label{sec:pipeline}

\subsection{Network Topology}

The Q-NarwhalKnight production network consists of three geographically distributed
servers behind an Nginx load balancer with TLS termination and IP-hash session affinity:

\begin{table}[H]
\centering
\caption{Server infrastructure specification}
\label{tab:servers}
\scriptsize
\begin{tabularx}{\columnwidth}{lXcc}
\toprule
\textbf{Server} & \textbf{Role} & \textbf{RAM} & \textbf{Weight} \\
\midrule
Alpha & Docker canary & 8~GB & -- \\
Beta  & Primary production & 94~GB & $w=10$ \\
Gamma & Backup / failover & 7.8~GB & $w=1$ \\
\bottomrule
\end{tabularx}
\end{table}

The Nginx upstream configuration uses weighted round-robin with \texttt{ip\_hash}
sticky sessions, ensuring that individual users consistently reach the same backend
throughout their session, preventing balance display flickering during rolling upgrades.

\subsection{Six-Stage Rolling Upgrade Protocol}

The deployment pipeline executes six atomic stages, each with a health verification
gate. The pipeline is implemented in \texttt{scripts/ha-deploy.sh} and can be
triggered via a single command or the GUI admin panel.

\begin{figure}[H]
\centering
\begin{tikzpicture}[
    node distance=0.5cm and 0.3cm,
    stage/.style={rectangle, draw=qnkblue, fill=qnkblue!8, text width=2.8cm,
                  minimum height=0.8cm, align=center, font=\scriptsize\bfseries,
                  rounded corners=2pt},
    arrow/.style={-{Stealth[length=4pt]}, thick, qnkblue},
    check/.style={circle, draw=qnkgreen, fill=qnkgreen!15, inner sep=1pt,
                  font=\scriptsize\bfseries, text=qnkgreen}
]
\node[stage] (s1) {Stage 1\\Verify Alpha};
\node[check, right=0.15cm of s1] (c1) {\checkmark};
\node[stage, below=0.3cm of s1] (s2) {Stage 2\\Verify Gamma};
\node[check, right=0.15cm of s2] (c2) {\checkmark};
\node[stage, below=0.3cm of s2] (s3) {Stage 3\\Promote Gamma};
\node[check, right=0.15cm of s3] (c3) {\checkmark};
\node[stage, below=0.3cm of s3] (s4) {Stage 4\\Soak Test (30s)};
\node[check, right=0.15cm of s4] (c4) {\checkmark};
\node[stage, below=0.3cm of s4] (s5) {Stage 5\\Deploy Beta};
\node[check, right=0.15cm of s5] (c5) {\checkmark};
\node[stage, below=0.3cm of s5] (s6) {Stage 6\\Restore Weights};
\node[check, right=0.15cm of s6] (c6) {\checkmark};

\draw[arrow] (c1) |- (s2.east);
\draw[arrow] (c2) |- (s3.east);
\draw[arrow] (c3) |- (s4.east);
\draw[arrow] (c4) |- (s5.east);
\draw[arrow] (c5) |- (s6.east);
\end{tikzpicture}
\caption{Six-stage rolling deployment pipeline. Each stage requires health
verification ($\checkmark$) before proceeding.}
\label{fig:pipeline}
\end{figure}

\noindent\textbf{Stage~1 -- Verify Alpha (Canary):} The release binary is SCP'd to
Server Alpha's Docker container. A non-blocking health check verifies the binary starts,
loads the database, and responds to API requests. Alpha never serves production traffic,
making this a zero-risk verification.

\noindent\textbf{Stage~2 -- Verify Gamma:} The binary is deployed to Gamma, the backup
node. Systemd restarts the service and the pipeline waits for the \texttt{/api/v1/status}
endpoint to return \texttt{"status": "ready"} with a matching version number.

\noindent\textbf{Stage~3 -- Promote Gamma:} Nginx weights are reconfigured:
$w_\text{Gamma} = 10$, $w_\text{Beta} = 1$. This atomically shifts 91\% of production
traffic to the newly-upgraded Gamma while Beta continues serving existing sessions.

\noindent\textbf{Stage~4 -- Soak Test:} A 30-second observation window monitors Gamma
under production load. The pipeline checks for error rates, block production continuity,
P2P connectivity, and SSE stream health.

\noindent\textbf{Stage~5 -- Deploy Beta:} With Gamma handling production traffic, Beta
is stopped, upgraded, and restarted. Health verification confirms the new version.

\noindent\textbf{Stage~6 -- Restore:} Nginx weights return to $w_\text{Beta} = 10$,
$w_\text{Gamma} = 1$, restoring the standard topology. Both servers now run the new
version.

\subsection{RAM-Adaptive Storage Engine (v6.0.3)}

A critical discovery during production operation was that Gamma's 7.8~GB RAM was
insufficient for the default RocksDB configuration, which allocated 2~GB block cache
plus $128~\text{MB} \times 6$ write buffers = 2.77~GB for database operations alone.
This caused 9 OOM kills over a 24-hour period.

Version 6.0.3 introduces automatic RAM detection using the \texttt{sysinfo} crate,
implementing five hardware tiers:

\begin{table}[H]
\centering
\caption{RAM-adaptive storage tiers}
\label{tab:ramtiers}
\scriptsize
\begin{tabularx}{\columnwidth}{lcccc}
\toprule
\textbf{Tier} & \textbf{RAM} & \textbf{Cache} & \textbf{WBuf} & \textbf{Count} \\
\midrule
Micro   & $\leq$4~GB  & 10\% & 32~MB  & 3 \\
Small   & 4--8~GB     & 15\% & 64~MB  & 4 \\
Medium  & 8--16~GB    & 20\% & 128~MB & 6 \\
Large   & 16--32~GB   & 25\% & 128~MB & 6 \\
XLarge  & $>$32~GB    & 25\% & 128~MB & 6 \\
\bottomrule
\end{tabularx}
\end{table}

The auto-tune reduced Gamma's RocksDB allocation from 2.77~GB to 1.26~GB, resulting
in a peak RSS of $\sim$6~GB (within the 7.8~GB + 4~GB swap envelope) versus the
previous 7.8~GB+ RSS that consistently triggered OOM kills.

\begin{lstlisting}[language=Rust,caption={RAM auto-detection in kv.rs}]
let total_ram_mb = {
    let mut sys = System::new_all();
    sys.refresh_memory();
    (sys.total_memory() / (1024 * 1024)) as usize
};
let ram_tier = match total_ram_mb {
    0..=3999   => "micro",
    4000..=7999 => "small",
    8000..=15999 => "medium",
    16000..=31999 => "large",
    _           => "xlarge",
};
\end{lstlisting}

\subsection{Pre-Flight Database Verification}

Before serving any requests, the node performs structural integrity verification:

\begin{enumerate}[nosep,leftmargin=*]
    \item \textbf{Chain continuity}: Verify the last 100 blocks have valid parent links
    \item \textbf{Height pointer consistency}: Confirm tip block matches stored height
    \item \textbf{Schema compatibility}: Validate column family versions
    \item \textbf{Block sampling}: Verify 1\% of blocks deserialize correctly
\end{enumerate}

This pre-flight check runs in $<$3 seconds for chains of 3.4M+ blocks and prevents
deployment of binaries with incompatible storage formats.

\subsection{Automatic Rollback}

If any stage fails, the pipeline executes automatic rollback:

\begin{lstlisting}[language=bash,caption={Emergency rollback procedure}]
./scripts/ha-deploy.sh rollback
# Restores previous binary from backup/
# Restarts service with known-good version
# Verifies health before exiting
\end{lstlisting}

Binary backups are created automatically before every deployment, ensuring that
rollback to the previous version is always possible within seconds.

% ============================================================================
% 3. Water Robot Architecture
% ============================================================================
\section{Water Robot Swarm Coordination}
\label{sec:waterrobots}

\subsection{Overview}

Water Robots are bio-integrated autonomous systems modeled as microfluidic droplets
(50--500 nL) containing DNA storage cores, protein processing units, and quantum
coherence fields. They coordinate through a multi-modal communication substrate
and participate in the Q-NarwhalKnight consensus via string-theoretic resonance.

\subsection{Species Taxonomy}

The system defines eight primary species optimized for distinct computational roles:

\begin{table}[H]
\centering
\caption{Water Robot species taxonomy}
\label{tab:species}
\scriptsize
\begin{tabularx}{\columnwidth}{lXc}
\toprule
\textbf{Species} & \textbf{Function} & \textbf{Volume} \\
\midrule
\textit{H. computaticus} & General computation & 50--100 nL \\
\textit{B. perpetuus}    & Long-term storage   & 200--500 nL \\
\textit{M. velocis}      & Inter-system comms  & 20--50 nL \\
\textit{R. globalis}     & System broadcasts   & 100--150 nL \\
\textit{E. aquaticus}    & Environmental sensing & 30--80 nL \\
\textit{P. systemicus}   & Security/threat resp. & 150--300 nL \\
\textit{M. economicus}   & Marketplace trading & 80--120 nL \\
\textit{C. abundantia}   & Resource harvesting & 100--200 nL \\
\bottomrule
\end{tabularx}
\end{table}

Two hybrid species emerge from inter-species cooperation: \textit{Scholar Droplets}
(Processor + Memory) and \textit{Diplomat Droplets} (Communication + Economic).

\subsection{String-Theoretic Resonance Consensus}

Each Water Robot is modeled as a vibrating string in a field-theoretic framework.
The state of robot $i$ at time $t$ is characterized by:

\begin{equation}
\psi_i(t) = A_i(t) \cdot \sin\!\left(2\pi f_i t + \phi_i\right)
\end{equation}

\noindent where $A_i = E_i \cdot h_i$ is the amplitude (energy $\times$ health),
$f_i = f_{\text{base}} \cdot q_i$ is the frequency (base oscillation $\times$
communication quality), and $\phi_i \in [0, 2\pi)$ is the formation phase.

\subsubsection{Coupling Energy}

The interaction between robots $i$ and $j$ is governed by a coupling energy:

\begin{equation}
V_{ij} = \begin{cases}
    \kappa \cdot A_i A_j \cos(\phi_i - \phi_j) \cdot e^{-d_{ij}/r_c} & d_{ij} \leq r_c \\
    0 & d_{ij} > r_c
\end{cases}
\end{equation}

\noindent where $\kappa = 0.5$ is the coupling strength, $d_{ij}$ is the Euclidean
distance, and $r_c = 10$ meters is the coupling radius.

\subsubsection{Swarm Energy Functional}

The total swarm energy functional is:

\begin{equation}
\mathcal{H} = \sum_i \frac{1}{2} A_i^2 (2\pi f_i)^2 + \sum_{i<j} V_{ij} + \gamma \sum_i \dot{A}_i^2
\end{equation}

\noindent where $\gamma = 0.1$ is the damping coefficient. Lower energy corresponds
to more stable configurations. The system evolves toward energy minima through
dissipative dynamics.

\subsubsection{Spectral Byzantine Fault Detection}

Byzantine robots are detected via spectral analysis of the swarm's Laplacian matrix:

\begin{equation}
L_{ij} = \begin{cases}
    \sum_{k \neq i} |V_{ik}| & i = j \\
    -|V_{ij}| & i \neq j
\end{cases}
\end{equation}

The spectral gap $\lambda_2 - \lambda_1$ between the two smallest eigenvalues
determines network connectivity. A gap below threshold $\epsilon = 0.01$ indicates
potential partitioning by Byzantine actors. Robots contributing disproportionately
to eigenvector components corresponding to small eigenvalues receive elevated
suspicion scores.

\subsubsection{K-Parameter Phase Transitions}

The K-parameter governs collective phase transitions:

\begin{equation}
K = \frac{\mathcal{H}}{N \cdot \bar{f} \cdot C}
\end{equation}

\noindent where $N$ is the robot count, $\bar{f}$ is the mean frequency, and
$C$ is the coherence score. When $K > K_{\text{crit}} = \varphi^2 \approx 2.618$
(the square of the golden ratio), the swarm undergoes a phase transition from
disordered to ordered consensus.

\subsection{Coherence Score}

The global coherence metric measures alignment across the swarm:

\begin{equation}
C = \frac{1}{N} \left| \sum_{i=1}^{N} e^{i\phi_i} \right|
\end{equation}

\noindent where $C = 0$ represents complete disorder and $C = 1$ represents
perfect phase alignment. The coherence score is tracked across consensus rounds
to detect degradation.

\subsection{Update Mechanism: Shadow Mode Integration}

Water Robot resonance operates in \textit{shadow mode} alongside the primary
DAG-BFT consensus:

\begin{enumerate}[nosep,leftmargin=*]
    \item For each consensus round $r$, update all robot string states from physical
          sensors and network metrics.
    \item Compute pairwise coupling energies $V_{ij}$ for all robot pairs within
          coupling radius.
    \item Build the Laplacian matrix $L$ and compute its spectrum.
    \item Flag robots with suspicion scores above threshold as potential Byzantine actors.
    \item Calculate the K-parameter and check for phase transitions.
    \item Determine resonance ordering (rank robots by energy contribution).
    \item Compare resonance ordering with DAG-BFT ordering and log agreement rate.
\end{enumerate}

The resonance weight parameter $w_r \in [0, 1]$ controls the influence of
resonance ordering on the final consensus output. In the current deployment,
$w_r = 0.10$ (10\% resonance influence), with plans to increase as the system
matures through phases.

\subsection{Communication Substrate}

Water Robots communicate through five channels:

\begin{table}[H]
\centering
\caption{Multi-modal communication channels}
\label{tab:comms}
\scriptsize
\begin{tabularx}{\columnwidth}{lXc}
\toprule
\textbf{Channel} & \textbf{Mechanism} & \textbf{Rate} \\
\midrule
FRET Signaling   & Optical (10--100 nm) & $10^6$ bps \\
Chemical Gradient & Molecular diffusion  & $10^3$ bps \\
Electrical Field  & Substrate electrodes & $10^5$ bps \\
Quantum Entangle. & Bell pair correlation & Instant \\
Bioluminescence   & Multi-freq. light    & $10^4$ bps \\
\bottomrule
\end{tabularx}
\end{table}

\subsection{OptiMart Decentralized Marketplace}

Resource allocation among Water Robots is governed by the OptiMart marketplace,
using a multi-token economy:

\begin{itemize}[nosep,leftmargin=*]
    \item \textbf{AquaUnits (AQU)} -- Primary currency, backed by computational work
    \item \textbf{DNA-Tokens (DNT)} -- Genetic sequence licenses
    \item \textbf{Energy-Tokens (ENT)} -- Metabolic energy credits
    \item \textbf{Compute-Tokens (CMT)} -- Processing power allocation
\end{itemize}

Price discovery follows: $P(t) = P_{\text{base}} \cdot \frac{D(t)}{S(t)} \cdot Q \cdot R$
where $Q$ is a quality multiplier and $R$ is species reputation.

\subsection{Evolutionary Protocols}

Water Robots evolve through four mechanisms operating simultaneously:

\begin{enumerate}[nosep,leftmargin=*]
    \item \textbf{Genetic}: Point mutations, insertions, recombination, horizontal transfer
    \item \textbf{Selection}: Computational efficiency, environmental adaptation, economic success
    \item \textbf{Behavioral}: Reinforcement, imitation, exploratory, and social learning
    \item \textbf{Systemic}: Network topology optimization, protocol efficiency, speciation
\end{enumerate}

% ============================================================================
% 4. Cross-Node Synchronization Analysis
% ============================================================================
\section{Cross-Node State Synchronization}
\label{sec:sync}

\subsection{Empirical Methodology}

We conducted a systematic comparison of API responses across the production
Beta and Gamma nodes on February~11, 2026. Both nodes were running v6.0.3
on \texttt{testnet-phase19}. Seven endpoint categories were tested, with responses
compared byte-for-byte where applicable.

\subsection{Results}

\begin{table}[H]
\centering
\caption{Cross-node API consistency (Feb 11, 2026)}
\label{tab:syncresults}
\scriptsize
\begin{tabularx}{\columnwidth}{lccX}
\toprule
\textbf{Endpoint} & \textbf{Beta} & \textbf{Gamma} & \textbf{Match} \\
\midrule
\texttt{/status}           & 200 & 200 & Partial\textsuperscript{1} \\
\texttt{/dex/pools}        & 200 & 200 & \textcolor{qnkgreen}{\textbf{100\%}} \\
\texttt{/dex/tokens}       & 200 & 200 & \textcolor{qnkgreen}{\textbf{100\%}} \\
\texttt{/oracle/prices}    & 200 & 200 & \textcolor{qnkgreen}{\textbf{100\%}} \\
\texttt{/blocks/3369000}   & 200 & 200 & \textcolor{qnkgreen}{\textbf{100\%}} \\
\texttt{/blocks/3400000}   & 404 & 200 & \textcolor{qnkred}{\textbf{Diverged}} \\
Block height               & 3.37M & 3.47M & \textcolor{qnkred}{\textbf{--104K}} \\
\bottomrule
\end{tabularx}
\\[4pt]
\scriptsize\textsuperscript{1}Version, network, upgrades match. Height differs.
\end{table}

\subsubsection{DeFi State: Perfect Synchronization}

All 12 DEX liquidity pools exhibited byte-identical reserves across both nodes.
All 32 supported tokens matched in metadata (symbol, decimals, address, type).
All 13 oracle prices were identical to 4 decimal places. This confirms that
the gossipsub-based DeFi state propagation is reliable and complete.

\begin{table}[H]
\centering
\caption{DEX pool reserve comparison (sample)}
\label{tab:pools}
\scriptsize
\begin{tabularx}{\columnwidth}{lrrX}
\toprule
\textbf{Pool} & \textbf{Reserve$_0$} & \textbf{Reserve$_1$} & \textbf{Match} \\
\midrule
QUG/QUGUSD  & 10,000.00 & 425,000.00 & \checkmark \\
SMOL/QUG    & 9,594.30  & 1,309.06   & \checkmark \\
BORK/QUG    & 161,340.50 & 1,244.66  & \checkmark \\
DOGE/QUG    & 195,207.87 & 1,028.80  & \checkmark \\
YOLO/QUG    & 1,399,989  & 715.00    & \checkmark \\
DERP/QUG    & 500,572.84 & 400.24    & \checkmark \\
\bottomrule
\end{tabularx}
\end{table}

\subsubsection{Block Consensus: Height Divergence}

The most significant finding was a 103,952-block height differential between
Beta (3,369,080) and Gamma (3,473,032). For blocks within both nodes' range,
data was byte-identical (verified at height 3,369,000: same \texttt{prev\_hash},
\texttt{state\_root}, \texttt{tx\_root}, and all 101 transactions).

The divergence is attributed to two factors:

\begin{enumerate}[nosep,leftmargin=*]
    \item \textbf{Memory-constrained sync stall}: Beta's block production
          and sync were disrupted during a period of high memory pressure,
          while Gamma continued receiving blocks via P2P.
    \item \textbf{Unidirectional catch-up}: The TurboSync protocol prioritizes
          forward sync (catching up to network height) but does not implement
          bidirectional height negotiation between peers.
\end{enumerate}

\subsubsection{Authenticated Endpoints: Untestable}

Balance queries, wallet state, and token holdings require session-based
authentication and cannot be tested via direct API calls. This represents
a significant gap in our synchronization verification capability. Future
work must implement authenticated cross-node consistency checks.

\subsection{Root Cause Analysis}

\subsubsection{State Categorization}

We categorize node state into four layers, each with different synchronization
characteristics:

\begin{table}[H]
\centering
\caption{State synchronization layers}
\label{tab:statelayers}
\scriptsize
\begin{tabularx}{\columnwidth}{lXcc}
\toprule
\textbf{Layer} & \textbf{Mechanism} & \textbf{Status} & \textbf{Latency} \\
\midrule
Blockchain    & P2P blocks, TurboSync & Partial & $<$5s \\
DeFi state    & Gossipsub replication  & Complete & $<$1s \\
User balances & Block-derived + P2P    & Unknown  & $<$15s \\
In-memory     & Not replicated         & None     & -- \\
\bottomrule
\end{tabularx}
\end{table}

\subsubsection{Memory Pressure as Root Cause}

Gamma's OOM kill cycle directly caused block production stalls:

\begin{enumerate}[nosep,leftmargin=*]
    \item RocksDB allocates 2.77~GB on a 7.8~GB system
    \item Sync operations consume additional memory for block buffers
    \item RSS exceeds 7.8~GB $\rightarrow$ swap usage reaches 100\%
    \item Linux OOM killer terminates the process
    \item Systemd restarts $\rightarrow$ process must re-sync from last checkpoint
    \item Repeat (9 OOM kills observed in 24 hours)
\end{enumerate}

The v6.0.3 RAM auto-tune reduces RocksDB allocation to 1.26~GB on Gamma,
breaking this cycle.

\subsubsection{Non-Replicated State}

Several state categories are computed locally and never propagated:

\begin{itemize}[nosep,leftmargin=*]
    \item Mining statistics (hashrate, accepted shares, per-miner tracking)
    \item SSE connection state (active subscribers, event queues)
    \item Price history indexer (candle data derived from swap events)
    \item AI inference coordinator state (worker registry, active requests)
\end{itemize}

These states are reconstructed from the blockchain on restart but may diverge
between nodes that have processed different sets of transactions.

% ============================================================================
% 5. Future Update Pipeline & Roadmap
% ============================================================================
\section{Remediation Roadmap}
\label{sec:roadmap}

We propose a four-phase plan to achieve full deterministic state synchronization
across all nodes.

\subsection{Phase I: Foundation (Q1 2026 -- Complete)}

\begin{table}[H]
\centering
\scriptsize
\begin{tabularx}{\columnwidth}{lXc}
\toprule
\textbf{Task} & \textbf{Description} & \textbf{Status} \\
\midrule
HA Pipeline & 3-server rolling deploy & \textcolor{qnkgreen}{Done} \\
RAM Auto-Tune & sysinfo-based RocksDB sizing & \textcolor{qnkgreen}{Done} \\
Memory Limiter & Pause sync under pressure & \textcolor{qnkgreen}{Done} \\
Pre-flight Check & DB integrity verification & \textcolor{qnkgreen}{Done} \\
DeFi Sync & Gossipsub pool/price replication & \textcolor{qnkgreen}{Done} \\
Upgrade Gate & Height-gated consensus rules & \textcolor{qnkgreen}{Done} \\
\bottomrule
\end{tabularx}
\end{table}

\subsection{Phase II: Block Consistency (Q2 2026)}

\begin{table}[H]
\centering
\scriptsize
\begin{tabularx}{\columnwidth}{lXc}
\toprule
\textbf{Task} & \textbf{Description} & \textbf{ETA} \\
\midrule
Bidirectional sync & Height negotiation between peers & Apr 2026 \\
State snapshot & Periodic full-state checkpoints & Apr 2026 \\
Balance audit & Cross-node balance verification & May 2026 \\
Authenticated test & API consistency test harness & May 2026 \\
Fork resolution & Automatic reorg detection + repair & Jun 2026 \\
\bottomrule
\end{tabularx}
\end{table}

\noindent\textbf{Bidirectional TurboSync}: Currently, nodes only sync
\textit{forward} (catching up to a higher peer). Phase~II introduces
bidirectional height negotiation where nodes periodically compare tip
hashes and trigger re-sync if they diverge, even at the same height.

\noindent\textbf{State Snapshots}: Full state snapshots (blockchain +
balances + token state + DEX pools) will be generated every 10,000 blocks
and distributed via P2P. New nodes can bootstrap from snapshots instead
of syncing the full chain.

\subsection{Phase III: Deterministic Replay (Q3 2026)}

\begin{table}[H]
\centering
\scriptsize
\begin{tabularx}{\columnwidth}{lXc}
\toprule
\textbf{Task} & \textbf{Description} & \textbf{ETA} \\
\midrule
State root hash & Merkle root of all balances per block & Jul 2026 \\
Deterministic VM & WASM-based transaction execution & Jul 2026 \\
Consensus proof & ZK-proof of state transition validity & Aug 2026 \\
Replay testing & Automated full-chain replay verification & Aug 2026 \\
Cross-node audit & Continuous balance comparison daemon & Sep 2026 \\
\bottomrule
\end{tabularx}
\end{table}

\noindent\textbf{State Root Hash}: Each block will include a Merkle root
computed from all account balances and token states. This enables any node
to verify that its state matches the network consensus by comparing roots.

\noindent\textbf{Deterministic Replay}: Given the same genesis state and
the same sequence of blocks, every node must arrive at exactly the same
balance state. This is the gold standard for blockchain consistency and
eliminates all classes of state divergence.

\subsection{Phase IV: Water Robot Integration (Q4 2026)}

\begin{table}[H]
\centering
\scriptsize
\begin{tabularx}{\columnwidth}{lXc}
\toprule
\textbf{Task} & \textbf{Description} & \textbf{ETA} \\
\midrule
Resonance weight ramp & Increase $w_r$ from 0.10 to 0.50 & Oct 2026 \\
Spectral BFT prod. & Deploy Byzantine detection live & Oct 2026 \\
Bio-consensus bridge & On-chain recording of swarm votes & Nov 2026 \\
Swarm state sync & P2P replication of robot state & Nov 2026 \\
Full integration & Resonance as primary ordering hint & Dec 2026 \\
\bottomrule
\end{tabularx}
\end{table}

\noindent\textbf{Resonance Weight Ramp}: As confidence in the resonance
consensus grows through shadow-mode validation, the resonance weight
$w_r$ will be gradually increased, giving the Water Robot swarm greater
influence over transaction ordering.

\subsection{Success Criteria}

The synchronization remediation is considered complete when:

\begin{enumerate}[nosep,leftmargin=*]
    \item All nodes within 10 blocks of network tip height (99.9\% uptime)
    \item State root hashes match across all nodes for every finalized block
    \item Authenticated API responses are byte-identical across nodes for
          the same block height
    \item Full-chain deterministic replay produces identical state on fresh nodes
    \item Water Robot resonance agrees with DAG-BFT ordering $>$95\% of rounds
\end{enumerate}

% ============================================================================
% 6. Conclusion
% ============================================================================
\section{Conclusion}

Q-NarwhalKnight v6.0.3 demonstrates that a post-quantum blockchain can operate
in production with zero-downtime upgrades across heterogeneous hardware. The
three-server rolling deployment pipeline has been validated through multiple
production deployments, and the RAM-adaptive storage engine has eliminated
OOM-induced failures on memory-constrained nodes.

Empirical analysis confirms that DeFi state synchronization achieves 100\%
consistency through gossipsub replication, while block-level consensus
requires additional work to handle height divergence under memory pressure.
The four-phase roadmap presented here provides a concrete path to full
deterministic state synchronization by Q4~2026.

The Water Robot swarm architecture represents a novel approach to bio-integrated
consensus, using string-theoretic resonance and spectral Byzantine fault
detection to complement traditional DAG-BFT. As the system matures through
shadow-mode validation, the resonance weight will increase, potentially
enabling a new class of consensus mechanisms that bridge biological and
digital computation.

% ============================================================================
% References
% ============================================================================
\section*{References}

\begin{enumerate}[nosep,leftmargin=*,label={[\arabic*]}]
    \item Danezis, G., Kokoris-Kogias, E., Sonnino, A., Spiegelman, A.
          ``Narwhal and Tusk: A DAG-based Mempool and Efficient BFT Consensus.''
          \textit{EuroSys}, 2022.
    \item Keidar, I., Kokoris-Kogias, E., Naor, O., Spiegelman, A.
          ``DAG-Knight: A Parameterless Generalization of Nakamoto Consensus.''
          \textit{arXiv:2203.13502}, 2022.
    \item Ongaro, D., Ousterhout, J. ``In Search of an Understandable Consensus
          Algorithm.'' \textit{USENIX ATC}, 2014.
    \item Church, G.M., Gao, Y., Kosuri, S. ``Next-Generation Digital Information
          Storage in DNA.'' \textit{Science}, 337(6102), 2012.
    \item Facebook/Meta. ``RocksDB: A Persistent Key-Value Store for Flash and
          RAM Storage.'' \url{https://rocksdb.org/}, 2013--2026.
    \item Protocol Labs. ``libp2p: Modular Peer-to-Peer Networking Stack.''
          \url{https://libp2p.io/}, 2017--2026.
    \item Quillon Research. ``Quantum Aesthetics in Consensus Systems: A
          K-Parameter Approach.'' Technical Report, 2025.
    \item Quillon Research. ``Water Robot Biological Programming: BioDSL
          Specification.'' Internal Document, 2026.
\end{enumerate}

\vspace{1em}
\noindent\rule{\columnwidth}{0.4pt}
\begin{center}
\scriptsize
\textcolor{gray}{Q-NarwhalKnight is developed by Quillon Research Laboratory.\\
Source: \texttt{https://quillon.xyz} \quad Network: \texttt{testnet-phase19}\\
This document was generated from production telemetry on February 11, 2026.}
\end{center}

\end{document}
