\documentclass[11pt,a4paper]{article}

\usepackage[margin=2.5cm]{geometry}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{array}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{fontenc}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{fancyhdr}
\usepackage{mdframed}

\definecolor{qugblue}{RGB}{30, 80, 160}
\definecolor{lightgray}{RGB}{245, 245, 245}

\hypersetup{
  colorlinks=true,
  linkcolor=qugblue,
  urlcolor=qugblue,
}

\titleformat{\section}{\large\bfseries\color{qugblue}}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\normalsize\bfseries}{}{0em}{}

\pagestyle{fancy}
\fancyhf{}
\rhead{\small\color{gray} Quillon Network — Confidential}
\lhead{\small\color{gray} QUGUSD Allocation Structure}
\rfoot{\small\thepage}

\begin{document}

% Title block
\begin{center}
  {\LARGE\bfseries QUGUSD Partnership Allocation}\\[0.4em]
  {\large\color{qugblue} Collateral Mechanics \& Conversion Path}\\[0.6em]
  {\small Dragon Ball Enterprise $\times$ Quillon Network \quad|\quad April 2026 \quad|\quad Confidential}
\end{center}

\vspace{0.5em}
\begin{mdframed}[backgroundcolor=lightgray, linecolor=qugblue, linewidth=1pt]
\small
\textbf{Summary.} Quillon commits 20,000,000 QUGUSD to the Dragon Ball FPGA/ASIC partnership.
QUGUSD is a collateralised debt position (CDP) stablecoin pegged 1:1 to USD,
backed by locked QUG at a 150\% minimum collateralisation ratio.
At the current QUG price of \$2,971, the allocation is overcollateralised.
Conversion to USDT runs through the HiBT exchange listing targeted for Q4 2026.
The liquidation mechanism protects the peg if QUG price falls.
All mechanics are on-chain and independently verifiable.
\end{mdframed}

\vspace{1em}

\section{What is QUGUSD}

QUGUSD is Quillon's native stablecoin. It is not issued by a central entity.
It is minted by locking QUG into an on-chain \texttt{CollateralVault} contract,
subject to a minimum collateralisation ratio of 150\%.
The peg is maintained algorithmically: the protocol monitors the QUG/USD oracle
price and triggers liquidations automatically when a vault falls below the
safety threshold.

QUGUSD is a first-class token type in Quillon's transaction format
(\texttt{TokenType::QUGUSD}), meaning the consensus layer — not a separate
smart contract — validates all stablecoin operations.
There is no issuer who can freeze or blacklist tokens.

\section{The 20M QUGUSD Allocation}

\begin{center}
\begin{tabular}{lrl}
\toprule
\textbf{Use} & \textbf{Amount (QUGUSD)} & \textbf{Purpose} \\
\midrule
ASIC NRE funding          & 10,000,000  & Mask set, design, prototyping \\
FPGA development fund     &    500,000  & Hardware, boards, engineering time \\
Marketing \& launch       &    500,000  & Product launch, mining outreach \\
Market making (HiBT)      &    100,000  & QUG/USDT liquidity on listing \\
Exchange listing fee      &     15,000  & HiBT listing (CMC \#38) \\
Treasury reserve          &  8,885,000  & Operations \& future 7nm tape-out \\
\midrule
\textbf{Total}            & \textbf{20,000,000} & \\
\bottomrule
\end{tabular}
\end{center}

Tranches are released on delivery milestones. The first tranche (2,000,000 QUGUSD)
transfers upon contract signing. Subsequent tranches release at BLAKE3 pipeline
validation, full SoC verification, and ASIC feasibility sign-off.

\section{Collateral Mechanics}

\subsection{Minting}

To back 20,000,000 QUGUSD at a 150\% collateralisation ratio, the vault
must hold at least:

\[
  \text{QUG required} = \frac{20{,}000{,}000 \times 1.50}{\$2{,}971}
  = \frac{30{,}000{,}000}{2{,}971} \approx 10{,}097 \text{ QUG}
\]

At the current circulating supply of 487,668 QUG, this represents 2.07\%
of all mined supply — a meaningful but non-destabilising commitment.

\subsection{Overcollateralisation Buffer}

The vault is initialised at a 200\% ratio, providing a 50 percentage point
buffer above the liquidation threshold:

\[
  \text{Initial QUG locked} = \frac{20{,}000{,}000 \times 2.00}{2{,}971}
  \approx 13{,}463 \text{ QUG}
\]

At \$2,971/QUG this locks approximately \$40,000,000 in collateral to back
\$20,000,000 in QUGUSD — a 2:1 overcollateralisation at issuance.

\subsection{Liquidation Protection}

If the QUG price falls, the vault's collateralisation ratio falls with it.
The protocol enforces the following thresholds:

\begin{center}
\begin{tabular}{lll}
\toprule
\textbf{Event} & \textbf{Ratio} & \textbf{Action} \\
\midrule
Healthy          & $>$ 150\% & No action \\
Margin call      & 150\%     & Vault owner alerted \\
Partial liquidation & 140\% & Protocol sells QUG to restore ratio \\
Full liquidation    & 120\% & Entire vault liquidated, QUGUSD redeemed \\
\bottomrule
\end{tabular}
\end{center}

At the 120\% full liquidation threshold, QUG would need to fall to:

\[
  P_{\text{liquidation}} = \frac{20{,}000{,}000 \times 1.20}{13{,}463}
  \approx \$1{,}782 \text{ per QUG}
\]

This represents a 40\% decline from current price before any principal loss
occurs. Partial liquidations begin at 150\%, giving the vault owner time to
add collateral before losses materialise.

\section{Conversion Path to USDT}

QUGUSD is convertible to USDT via two routes:

\textbf{Route 1 — Quillon DEX (available now).}
QUGUSD trades on the native AMM at \texttt{quillon.xyz} with a live
QUG/QUGUSD pool. Conversion requires first swapping QUGUSD to QUG,
then QUG to USDT once QUG is listed externally.

\textbf{Route 2 — HiBT Exchange (Q4 2026).}
Quillon has a signed listing agreement with HiBT (CoinMarketCap rank \#38,
3.5M users). Once QUG/USDT is live on HiBT, QUGUSD is redeemable
directly via the DEX at the 1:1 peg and the resulting QUG is immediately
sellable for USDT. The first deposit of 5,000 USDT toward the listing fee
is scheduled for October 2026.

Route 2 is the primary liquidation path for large tranches. Dragon Ball
should plan USDT conversion timelines around the Q4 2026 listing date.
For smaller amounts, Route 1 is available now for operational expenses
denominated in QUGUSD.

\section{Price Sensitivity Analysis}

\begin{center}
\begin{tabular}{rrrr}
\toprule
\textbf{QUG Price} & \textbf{Collateral Value} & \textbf{Ratio} & \textbf{Status} \\
\midrule
\$2,971 (today)  & \$40,000,000 & 200\% & Healthy \\
\$2,230          & \$30,000,000 & 150\% & Margin call \\
\$1,975          & \$26,580,000 & 133\% & Partial liquidation \\
\$1,782          & \$24,000,000 & 120\% & Full liquidation \\
\$1,000          & \$13,463,000 & ---  & Post-liquidation \\
\bottomrule
\end{tabular}
\end{center}

At full liquidation (\$1,782/QUG), Dragon Ball's QUGUSD holdings are redeemed
at par (1:1 USD) from the liquidation proceeds. The 20M face value of the
allocation is preserved through the liquidation mechanism; only a QUG price
below the liquidation floor combined with a DEX liquidity failure would
result in a shortfall.

\section{Verification}

All vault mechanics are on-chain and auditable:

\begin{itemize}
  \item \textbf{Vault state:} \texttt{/api/v1/vaults/\{address\}} — returns
    collateralisation ratio, locked QUG, minted QUGUSD, liquidation price
  \item \textbf{Oracle price:} \texttt{/api/v1/oracle/qugusd} — live
    QUG/USD feed with multi-exchange consensus and outlier rejection
  \item \textbf{Supply audit:} \texttt{/api/v1/tokens/qugusd/supply} —
    total minted vs total collateral, always public
  \item \textbf{DEX pool:} \texttt{/api/v1/dex/pools} — live reserve
    depth for QUG/QUGUSD pair
\end{itemize}

Dragon Ball's technical team can verify any of these endpoints at any time
without relying on Quillon's representations.

\section{Summary}

\begin{center}
\begin{tabular}{ll}
\toprule
\textbf{Parameter} & \textbf{Value} \\
\midrule
Total allocation          & 20,000,000 QUGUSD \\
Peg                       & 1 QUGUSD = 1 USD \\
Collateral asset          & QUG \\
Current QUG price         & \$2,971 \\
Collateralisation at issuance & 200\% \\
QUG locked                & $\approx$13,463 QUG \\
Liquidation price         & \$1,782/QUG ($-$40\% from today) \\
Primary conversion path   & HiBT listing Q4 2026 \\
First tranche             & 2,000,000 QUGUSD on contract signing \\
On-chain verification     & Yes — all endpoints public \\
\bottomrule
\end{tabular}
\end{center}

\vspace{2em}
\hrule
\vspace{0.5em}
{\small\color{gray}
Quillon Network \quad|\quad \texttt{quillon.xyz} \quad|\quad April 2026 \quad|\quad
This document is provided for informational purposes to Dragon Ball Enterprise as part of the FPGA/ASIC partnership discussion.
It does not constitute a securities offering.
QUGUSD mechanics are subject to on-chain governance and may be updated by protocol upgrade.
}

\end{document}
